Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach

### 2016-06-03 main.tex
add PB CPSX affiliation

\title[SOM: classifying high $Z$ galaxies]{Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach} %PB160426: suggest "Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach" -- I think if you say "clustering galaxies" people will think of spatial clustering
\author{rahmani.sahar }
\date{\today}
\author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1}$\thanks{E-mail:
srahma49@uwo.ca}, H.~Teimoorinia$^{2}$, P.~Barmby$^{1}$\\
$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
$^{2}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada}
\maketitle

>>>>

\title[SOM: classifying high $Z$ galaxies]{Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach} %PB160426: suggest "Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach" -- I think if you say "clustering galaxies" people will think of spatial clustering
\author{rahmani.sahar }
\date{\today}
\author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1,2}$\thanks{E-mail:
srahma49@uwo.ca}, H.~Teimoorinia$^{2}$, P.~Barmby$^{1,3}$\\
$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
$^{2}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada\\
$^{3}$Center for Planetary Science \& Exploration, Western University}
\maketitle
